Learning and Recognition of \strips\ Action Models from State Observations \\ Action Model Recognition from State Observations via Planning

### 2018-01-22 doc/ijcai-18/observations-learning.tex
added last results generated by Diego

@@

\begin{table}
	\begin{center}
		\begin{scriptsize}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.57 & 0.44 & 0.63 & 0.56 & 0.57 & 0.44 & 0.59 & 0.48 \\
				driverlog & 0.2 & 0.07 & 0.18 & 0.29 & 0.2 & 0.14 & 0.19 & 0.17 \\
				ferry & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				floor-tile & 0.5 & 0.14 & 0.75 & 0.55 & 0.6 & 0.27 & 0.62 & 0.32 \\
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 0.25 & 0.17 & 0.25 & 0.25 & 0.25 & 0.25 & 0.25 & 0.22 \\
				hanoi & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				n-puzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				parking & 0.6 & 0.21 & 0.14 & 0.11 & 0.4 & 0.22 & 0.38 & 0.18 \\
				satellite & 0.25 & 0.07 & 0.33 & 0.4 & 0.67 & 0.5 & 0.42 & 0.32 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 0.33 & 0.1 & 0.33 & 0.4 & 0.0 & 0.0 & 0.22 & 0.17 \\
				zeno-travel & 0.25 & 0.07 & 0.17 & 0.14 & 0.0 & 0.0 & 0.14 & 0.07 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained when learning from labels without computing the $f_{P\&R}$ mapping.}
	\label{fig:labelsnomap}

	\begin{center}
		\begin{scriptsize}
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline
				blocks & 0.71 & 0.56 & 0.75 & 0.67 & 0.71 & 0.56 & 0.73 & 0.59 \\
				driverlog & 0.6 & 0.21 & 0.27 & 0.43 & 0.6 & 0.43 & 0.49 & 0.36 \\
				ferry & 0.5 & 0.29 & 0.75 & 0.75 & 0.5 & 0.5 & 0.58 & 0.51 \\
				floor-tile & 0.5 & 0.14 & 0.75 & 0.55 & 0.6 & 0.27 & 0.62 & 0.32 \\
				Grid & - & - & - & - & - & - & - & - \\ % Segmentation fault
				gripper-strips & 1.0 & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 \\
				hanoi & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				hiking & - & - & - & - & - & - & - & - \\ % Time out 1000s
				n-puzzle & - & - & - & - & - & - & - & - \\ % Time out 1000s
				parking & 0.6 & 0.21 & 0.14 & 0.11 & 0.4 & 0.22 & 0.38 & 0.18 \\
				satellite & 0.25 & 0.07 & 0.33 & 0.4 & 0.67 & 0.5 & 0.42 & 0.32 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 1.0 & 0.3 & 0.67 & 0.8 & 0.67 & 0.4 & 0.78 & 0.5 \\
				zeno-travel & 0.5 & 0.14 & 0.5 & 0.43 & 0.33 & 0.14 & 0.44 & 0.24 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained when learning from labels but computing the $f_{P\&R}$ mapping.}
	\label{fig:labels}
\end{table}

\begin{table}
	\begin{footnotesize}
		\begin{center}
			\begin{tabular}{l|c|c|c|}			
				& Total time & Preprocess & Plan length  \\
				\hline
				Blocks & 1.40 & 0.00 & 70  \\
				Driverlog & 1.50 & 0.00 & 89 \\
				Ferry & 1.49 & 0.00 & 64 \\
				Floortile & 351.38 & 0.11 & 156 \\
				Grid & - & - & - \\ % Segmentation fault
				Gripper & 0.04 & 0.00 & 59 \\
				Hanoi & 2.33 & 0.01 & 49  \\
				Hiking & - & - & - \\ % Time out 1000s
				Parking & - & - & - \\ % Time out 1000s
				Satellite & 78.36 & 0.03 & 98 \\
				Sokoban & - & - & - \\ % Time out 1000s
				Transport & 285.61 & 0.10 & 106 \\
				Zenotravel & 6.20 & 0.46 & 71 \\
			\end{tabular}
		\end{center}
	\end{footnotesize}
 \caption{\small Planning results obtained when learning from labels.}
\label{fig:planlabels}
\end{table}

>>>>

\subsubsection{Unsupervised evaluation of the learned models}

@@

\begin{table}
	\begin{center}
		\begin{scriptsize}                
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline

				blocks & 0.44 & 0.44 & 0.44 & 0.44 & 0.44 & 0.44 & 0.44 & 0.44 \\
				driverlog & 0.0 & 0.0 & 0.25 & 0.43 & 0.0 & 0.0 & 0.08 & 0.14 \\
				ferry & 1.0 & 0.71 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.9 \\
				floor-tile & 0.38 & 0.55 & 0.4 & 0.18 & 0.56 & 0.45 & 0.44 & 0.39 \\
				grid & 0.5 & 0.47 & 0.33 & 0.29 & 0.25 & 0.29 & 0.36 & 0.35 \\
				gripper-strips & 0.83 & 0.83 & 0.75 & 0.75 & 0.75 & 0.75 & 0.78 & 0.78 \\
				hanoi & 0.5 & 0.25 & 0.5 & 0.5 & 0.0 & 0.0 & 0.33 & 0.25 \\
				hiking & 0.43 & 0.43 & 0.5 & 0.35 & 0.44 & 0.47 & 0.46 & 0.42 \\
				miconic & 0.6 & 0.33 & 0.33 & 0.25 & 0.33 & 0.33 & 0.42 & 0.31 \\
				n-puzzle & 0.33 & 0.33 & 0.0 & 0.0 & 0.0 & 0.0 & 0.11 & 0.11 \\
				parking & 0.25 & 0.21 & 0.0 & 0.0 & 0.0 & 0.0 & 0.08 & 0.07 \\
				pegsol & - & - & - & - & - & - & - & - \\ % Time out 1000s
				satellite & 0.6 & 0.21 & 0.8 & 0.8 & 1.0 & 0.5 & 0.8 & 0.5 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 1.0 & 0.3 & 0.8 & 0.8 & 1.0 & 0.6 & 0.93 & 0.57 \\
				grid-visit-all & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 \\
				zeno-travel & 0.67 & 0.29 & 0.33 & 0.29 & 0.33 & 0.14 & 0.44 & 0.24 \\
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained without computing the $f_{P\&R}$ mapping.}
	\label{fig:observationsnomap}

	\begin{center}
		\begin{scriptsize}                
			\begin{tabular}{l|l|l|l|l|l|l||l|l|}
				& \multicolumn{2}{|c|}{\bf Pre} & \multicolumn{2}{|c|}{\bf Add} & \multicolumn{2}{|c||}{\bf Del} & \multicolumn{2}{|c}{\bf}\\ \cline{2-9}			
				& \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} & \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c||}{\bf R} &  \multicolumn{1}{|c|}{\bf P} & \multicolumn{1}{|c|}{\bf R} \\
				\hline

				blocks & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
				driverlog & 0.67 & 0.14 & 0.33 & 0.57 & 0.67 & 0.29 & 0.56 & 0.33 \\
				ferry & 1.0 & 0.71 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.9 \\
				floor-tile & 0.44 & 0.64 & 1.0 & 0.45 & 0.89 & 0.73 & 0.78 & 0.61 \\
				grid & 0.63 & 0.59 & 0.67 & 0.57 & 0.63 & 0.71 & 0.64 & 0.62 \\
				gripper-strips & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
				hanoi & 1.0 & 0.5 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.83 \\
				hiking & 0.78 & 0.6 & 0.93 & 0.82 & 0.88 & 0.88 & 0.87 & 0.77 \\
				miconic & 0.8 & 0.44 & 1.0 & 0.75 & 1.0 & 1.0 & 0.93 & 0.73 \\
				n-puzzle & 0.67 & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 & 0.89 \\
				parking & 0.56 & 0.36 & 0.5 & 0.33 & 0.5 & 0.33 & 0.52 & 0.34 \\
				pegsol & - & - & - & - & - & - & - & - \\ % Time out 1000s
				satellite & 0.6 & 0.21 & 0.8 & 0.8 & 1.0 & 0.5 & 0.8 & 0.5 \\
				Sokoban & - & - & - & - & - & - & - & - \\ % Time out 1000s
				transport & 1.0 & 0.3 & 1.0 & 1.0 & 1.0 & 0.6 & 1.0 & 0.63 \\ 
				grid-visit-all & 0.67 & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 & 0.89 & 1.0 \\
				zeno-travel & 1.0 & 0.43 & 0.67 & 0.57 & 1.0 & 0.43 & 0.89 & 0.48 \\                                
				\hline
				\bf  & - & - & - & - & - & - & - & - \\
			\end{tabular}
		\end{scriptsize}
	\end{center}
	\caption{\small Precision and recall values obtained when computing the $f_{P\&R}$ mapping.}
	\label{fig:observationsmap}                
\end{table}

\begin{table}
		\begin{center}
			\begin{tabular}{l|l|l|l|}
				& $\delta(\Xi,\mathcal{O})$ & $\delta(\Xi,*)$ & $P(\mathcal{O}|\Xi)$ \\
				\hline
				block & 0 & 90 & 1.0 \\
				ferry & 2 & 69 & 0.97 \\
				grid & 42 & 153 & 0.73 \\
				gripper & 2 & 30 & 0.93 \\
				hanoi & 1 & 63 & 0.98 \\
				miconic & 3 & 72 & 0.96 \\
				npuzzle & 2 & 24 & 0.92 \\
				transport & 4 & 78 & 0.95 \\
				visitall & 2 & 24 & 0.92 \\
				zenotravel & 3 & 63 & 0.95 \\
				\hline
				\bf  & - & - & - \\
			\end{tabular}
		\end{center}
	\caption{\small $P(\mathcal{O}|\Xi)=1-\frac{\delta(\Xi,\mathcal{O})}{\delta(\Xi,*)}$}
	\label{fig:observationstest}                
\end{table}
